---
title: "Check Regression Line- Comparison of Petal and Sepal Lengths / Widths"
author: "Claire"
date: "2020-01-22"
output: pdf_document
---

First, we set our working directory (varies based on your path):
```{r}
#setwd("C:/Users/frase/Documents/Rclass/Regression-repo")
```

We read in the desired dataset:
```{r}
read.csv("iris.csv")
```

**We then created a function that plots a dataset along with the x points along the line of regression. Then, we wanted to find the difference in y from the actual point to regression line. With this value, the sum of squared errors (sse) is calculated. Finally, the sse, slope, and y-intercept are added to the plot.**
```{r}
plotwithreg <- function(x, y, title, cxlab, cylab) {
plot(x, y, pch=10, col=iris$Species, main=title, xlab=cxlab, ylab=cylab)
lengths.lm <- lm(y~x) 
coef(lengths.lm)
b <- coef(lengths.lm)
int <- b[1]
slope <- b[2]
abline(lengths.lm, col="blue")

yhat <- slope*x + int
points(x, yhat)
segments(x, y, x, yhat)

error <- yhat - y #error in y from actual point to point on regression line
error^2
sse <- sum(error^2)
sse #obtain sum of squared errors

text(7.5,2, paste("sse=", sse))
text(7.5,1.5, paste("slope=", slope))
text(7.5,1, paste("intercept=", int))
legend("topleft", legend=levels(iris$Species), col= c(1,2,3), pch=10)
}
```

I named the objects for the variables that I wanted to test:
```{r}
Slength <- iris$Sepal.Length
Plength <- iris$Petal.Length
```

*Finally, I set x, y, and the labels and used the function we made!*
```{r}
x <- Slength
y <- Plength
plotwithreg(Slength, Plength, "Sepal and Petal Morph", "Sepal Length", "Petal Length")
```


# My Function: Normalize/Correct For

*I wanted to make a function that corrected the petal width by petal length.*
First, I named the required objects:
```{r}
Species <- iris$Species
Plength <- iris$Petal.Length
Pwidth <- iris$Petal.Width
```

Then, I created a function called norm that divided the y values by a set length(leng) and plots the results per species.
```{r}
norm <- function(x=Species, y, title, cxlab, cylab) {
y <- y/leng
plot(Species, y, main=title, xlab=cxlab, ylab=cylab, col= c(5,6,7))
}
```

Finally, the lengths(leng) are defined and vectors for x, y, and labels are used in the norm function.
```{r}
leng <- Plength
norm(Species, Pwidth, "Normalized Petal Widths to Lengths", "Species", "Petal")
```
